% Acknowledgements
\acknowledgements


\setlength {\parindent} {3em} 

I wish to express my sincere thanks to \textbf{Dr. Vanitha, M.D.}, Dean, Mahatma Gandhi  Memorial Government General Hospital \& K.A.P.V Government Medical College, Trichy for permitting me to use the resources of this institution for my study. \par

I owe my heartfelt gratitude and sincere thanks to my guide \textbf {Dr. K. Lakshmi, M.D.}, Associate Professor, Department of Microbiology for her valuable suggestions, guidance, constant support, motivation and encouragement throughout this study. \par

Sincere thanks to Former Professor \textbf {Dr. S. Dhanapaul M.D., D.M.V.}, Department of Microbiology for his constant encouragement and support during this work. \par

%My Sincere thanks to Dr.C.Margaret M.D., Professor ,Department of Hematology, Dr.Mayil vahanan.M.D ,Director, Institute of Internal Medicine and Dr.Kalaichelvi .M.D.DM., Professor and Head of the Department, Department of Medical Oncology for their constant encouragement and support during my study.

%I would like to thank all my Professors Dr.S.Thasneem Banu M.D., Dr.U.Umadevi M.D., and Dr.R.VANAJA M.D., for their support during this study.

I extend my gratitude to my co-guide \textbf {Dr. Vanathi M.D.}, Assistant
Professor, Department of Microbiology for her valuable guidance and constant support in this study. \par

%I extend my gratitude to my former co-guide Dr.R.DEEPA
%M.D.,Assistant Professor, Institute of Microbiology for her valuable guidance and
%constant support in this study.

I wish to extend my thanks to our Assistant Professors \textbf {Dr.Lavanya.R M.D., Dr.Kogilapriya M.D., Dr. Bhuvaneshwari M.D., Dr. Beulah M.D.,} for their support. \par

%I wish to extend my thanks to our former Assistant Professors Dr.N.Rathna priya M.D., Dr.K.Ushakrishnan M.D., Dr.Sripriya.C.S M.D., Dr. David Agatha M.D., Dr.B.Natesan M.D.DLO., for their support.

I would like to extend my thanks to all my postgraduate colleagues and technicians for their constant support and help in this study. \par

I am thankful to my dear parents, in-laws for their unconditioned love,
sacrifice and constant emotional support. I thank my wife \textbf {Dr. Aishwarya S, M.D.,} and my son \textbf {Viyan E} for their constant motivation, emotional support and help in completing the dissertation work. \par

I would like to thank the Institutional Ethics Committee, K.A.P.V Government Medical
college for approving my study. \par

Last but not least, I would like to thank the patients participated in this
study for their co-operation and support. \par
